---
title: "Assignment 2 Exercise 1 Function Explanation"
author: "Songying Chen"
date: "Oct 24 2023"
output: html_document
---

This is the document for explaining the insights of the function fertility_rate.

## The 1st Edition of Function
The first edition of the function doesn’t include the second argument. And the main point of the first function is to get the real fertility rate of Swiss based on the dataset “swiss”.

The following code shows how the first edition of the function works.

```{r, include=FALSE}
library(dplyr)
data("swiss")
force(swiss)
```

```{r, function1, echo=TRUE}
#set a function to get the real fertility rate of Swiss
fertility_rate <- function(data){
  #divide the old variable by 100 and plus 1 to get the meaningful fertility rate
    data$Fertility = data$Fertility/100 + 1 
  return(data$Fertility) #return the new data set
}
```
If I input the data set “swiss”, the follwing list is the result of the function that displays the true fertility rate in a right scale.

```{r}
fertility_rate(swiss)
```

## The 2nd edition of the function

The second edition mainly use the second argument as a tool. The second argument means the warning line or caution line of fertility rate, usually set as 1.5. The second edition of function is to create a new variable that indicates whether the fertility rate in certain province is under the caution line.

In the second function, the output shows a new data set with a new variable called under_caution, indicating whether the fertility rate is under caution line. If the fertility rate of certain province is under the caution line, the variable will be 1, otherwise it will be 0.

```{r, function2, echo=TRUE}
fertility_rate <- function(data,caution){
  #divide the old variable by 100 and plus 1 to get the meaningful fertility rate
    data$Fertility = data$Fertility/100 + 1 
  #creat a new variable to see if the fertility rate is above caution rate
  data <- mutate(data, under_caution = ifelse(Fertility > caution, 0, 1))
  return(data) #return the new data set
}
```
The follwoing data set is a new one based on the second argument “caution”. The input of the function is (swiss, caution = 1.5). So the data shows the true fertility rate as well as whether the fertility rate is under 1.5.
```{r}
fertility_rate(swiss,1.5)
```

